Initial Biome Composition Analysis

### 2018-06-13 Initial Community Composition.Rmd
Revert "Merge remote-tracking branch 'origin/master'"
This reverts commit 2b74d51665915358512166bea2bd177661db81aa.
Auto stash before revert of "Merge remote-tracking branch 'origin/master'"
Slow progress. Hunting for fixes takes me some time as I am also familiarizing

```{r setup, include=FALSE}
knitr::opts_knit$set(echo = TRUE, warning = TRUE)

#set working directory
setwd("C:/Users/Timothy Brennhofer/Desktop/KBS REU/KBS Data")
getwd()

@@

#load data
abun_raw <- fread("2016_10_13_run2_otus.csv")
abun <- abun_raw
abun[345,4719] <- 0
abun <- abun %>%
  select(-Run, -Day, -Reads) %>%
  rename(Cage = `Cage#`) %>%
  gather(otu, abun, -SampleID, -Cage, - Abx, -Dose, -Hour, -Cohoused, -Pair) %>%
  group_by(SampleID) %>%
  mutate(abun = abun/sum(abun), otu = as.numeric(otu)) %>%
  mutate(mouseid = paste(Cage, Abx, sep = "_")) %>%
  ungroup()

@@

#Create graph to demonstrate initial compositions
tempz <- abun_tax %>%
  group_by(mouseid, Phylum) %>%
  group_by(mouseid) %>%
  mutate(total = sum(abun))

ggplot(tempz, aes(x = mouseid, y = total, fill = Phylum)) +
  geom_bar()

>>>>

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = "C:/Users/Timothy Brennhofer/Desktop/KBS REU/KBS Data", echo = TRUE, warning = TRUE)

#set working directory
require(knitr)
opts_knit$set(root.dir = "C:/Users/Timothy Brennhofer/Desktop/KBS REU/KBS Data")
setwd("C:/Users/Timothy Brennhofer/Desktop/KBS REU/KBS Data")
getwd()

@@

#load data
abun_raw <- fread("C:/Users/Timothy Brennhofer/Desktop/KBS REU/KBS Data/2016_10_13_run2_otus.csv")
abun <- abun_raw
abun[345,4719] <- 0
abun <- abun %>%
  select(-Run, -Day, -Reads) %>%
  rename(Cage = `Cage#`) %>%
  gather(otu, abun, -SampleID, -Cage, - Abx, -Dose, -Hour, -Cohoused, -Pair) %>%
  group_by(SampleID) %>%
  mutate(abun = abun/sum(abun), otu = as.numeric(otu)) %>%
  mutate(mouseid = paste(Cage, Abx, sep = "_")) %>%
  ungroup()

@@

#Create graph to demonstrate initial compositions
tempz <- abun_tax %>%
  group_by(mouseid, Phylum) %>%
  filter(abun > .00001) %>%
  mutate(percentabun = paste0(round(100 *abun, 4), "%"))

tempz <- tempz[order(mouseid, Phylum),]

ggplot(tempz, aes(x = mouseid, y = percentabun, fill = Phylum)) +
  geom_bar(stat = "identity")
